---
title: "README: `rpom` package "
output: github_document
knit: (function(inputFile, encoding) {
        rmarkdown::render(inputFile,
                          encoding = encoding, 
                          output_dir = here::here())
      })
---

# Installation

The `rpom` package can be installed with the following script:

```{r installation, eval = FALSE}
#install.packages("remotes")
remotes::install_github("aterui/rpom")
```

# Overview

The R package `rpom` provides functions to yield analytical/numerical solutions for food chain length in branching river networks.

# Example

`fcl()` returns analytical solution of food chain length with specified values of ecosystem size (`size`) and branching rate (`lambda`).
This function does not allow any top down effects.

```{r fcl}
## generate a food web with preferential prey model
fwb <- ecotools::ppm(n_species = 10, n_basal = 3, l = 10, theta = 1)

## fcl
rpom::fcl(fwb, lambda = 0.1, size = 10)

```

`nfcl()` returns numerical solution of food chain length.
This function allows top down effects.

```{r nfcl}
## fcl
rpom::nfcl(fwb, lambda = 0.1, size = 10)

```

